An alternative to contextuality

### 2016-07-05 finalPaper.tex
the abstract
updated the implications section + added something in the git ignore file
minor fixes, the biblio had issues and fixed the abstract

\affiliation{Indian Institute of Science Education and Research (IISER), Mohali}
\begin{abstract}
We reconsider the no-go theorems on hidden variables and conclude
that the notion of contextuality is not a necessary feature of quantum
mechanics. We provide an alternative view, motivated by consistency
requirements between Bohmian Mechanics and the said theorems. This
is accomplished by identifying a new classical property, we call `multiplicativity'.
We propose a non-contextual hidden variable model, consistent with
all predictions of QM (for discrete spaces). Advantages of this view
are illuminated by discussion of implications of non-multiplicativity
to non-locality and its relation to contextuality.
\end{abstract}
\maketitle

@@

\bibliographystyle{apsrev4-1}
\bibliography{references}

>>>>

\affiliation{Indian Institute of Science Education and Research (IISER), Mohali}
\begin{abstract}
We propose a non-contextual hidden variable model, consistent with all predictions of QM (for discrete spaces). We reconsider the no-go theorems on hidden variables and conclude that the notion of contextuality is not a necessary feature of quantum mechanics. Motivated by consistency requirements between Bohmian Mechanics and the said theorems, we provide an alternative view. This is accomplished by identifying a new classical property, we call `multiplicativity'. Advantages of this view are illustrated by considering the implications of non-multiplicativity to non-locality and its relation to contextuality.
\end{abstract}
\maketitle

@@

TODO: Complete this part.
\bibliographystyle{apsrev4-1}
\bibliography{references}
